|

### 2023-05-17 paper/00-main.Rmd
arxiv submission

---
title: |
  | Get Strained: Analyzing Pass Rush in American Football with Player Tracking Data

@@

authors: 
- name: Quang Nguyen
  # thanks: Corresponding author's email
  affiliation: |
    | Department of Statistics & Data Science
    | Carnegie Mellon University
- name: Ronald Yurko
  affiliation: |
    | Department of Statistics & Data Science
    | Carnegie Mellon University
- name: Gregory J. Matthews
  affiliation: |
    | Department of Mathematics and Statistics
    | Loyola University Chicago

keywords:
- tracking data
- football
- pass rush
- statistics in sports

abstract: |
  In American football, a pass rush is an attempt by the defensive team to disrupt the offense and prevent the quarterback (QB) from completing a pass. Existing metrics for assessing pass rush performance are either discrete-time quantities or based on subjective judgement. Using player tracking data, we propose STRAIN, a novel metric for evaluating pass rushers in the National Football League (NFL) at the continuous-time within-play level. Inspired by the concept of strain rate in materials science, STRAIN is a simple and interpretable means for measuring defensive pressure in football. It is a directly-observed statistic as a function of two features: the distance between the pass rusher and QB, and the rate at which this distance is being reduced. Our metric possesses great predictability of pressure and stability over time. We also fit a multilevel model for STRAIN to understand the defensive pressure contribution of every pass rusher at the play-level. We apply our approach to NFL data and present results for the first 8 weeks of the 2021 season. In particular, we provide comparisons of STRAIN for different defensive positions and play outcomes, and rankings of the NFL's best pass rushers according to our metric.

bibliography: bibliography.bib
biblio-style: chicago
output: rticles::asa_article
header-includes:
  # \usepackage{mathptmx}
  # \renewcommand{\arraystretch}{0.8}
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  # fig.pos = "ht",
  cache = TRUE
)
library(here)
library(tidyverse)
```

>>>>

---
title: |
  | Here Comes the STRAIN: Analyzing Defensive Pass Rush in American Football with Player Tracking Data

@@

authors: 
- name: Quang Nguyen
  # thanks: Corresponding author's email
  affiliation: |
    | Department of Statistics & Data Science
    | Carnegie Mellon University
- name: Ronald Yurko
  affiliation: |
    | Department of Statistics & Data Science
    | Carnegie Mellon University
- name: Gregory J. Matthews
  affiliation: |
    | Department of Mathematics and Statistics
    | Center for Data Science and Consulting
    | Loyola University Chicago

keywords:
- American football
- defensive linemen
- multilevel model
- player tracking data

abstract: |
  In American football, a pass rush is an attempt by the defensive team to disrupt the offense and prevent the quarterback (QB) from completing a pass. Existing metrics for assessing pass rush performance are either discrete-time quantities or based on subjective judgement. Using player tracking data, we propose STRAIN, a novel metric for evaluating pass rushers in the National Football League (NFL) at the continuous-time within-play level. Inspired by the concept of strain rate in materials science, STRAIN is a simple and interpretable means for measuring defensive pressure in football. It is a directly-observed statistic as a function of two features: the distance between the pass rusher and QB, and the rate at which this distance is being reduced. Our metric possesses great predictability of pressure and stability over time. We also fit a multilevel model for STRAIN to understand the defensive pressure contribution of every pass rusher at the play-level. We apply our approach to NFL data and present results for the first eight weeks of the 2021 regular season. In particular, we provide comparisons of STRAIN for different defensive positions and play outcomes, and rankings of the NFL's best pass rushers according to our metric.

bibliography: bibliography.bib
output: rticles::asa_article
---

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.pos = "p"
  #cache = TRUE
)
library(here)
library(tidyverse)
```

### 2023-05-17 paper/01-introduction.Rmd
arxiv submission

In recent years, tracking data have replaced traditional box-score statistics and play-by-play data as the state of the art in sports analytics.
Numerous sports are collecting and releasing data on player and ball locations on the playing surface over the course of a game.
This multi-resolution, spatio-temporal source of data has provided exceptional opportunities for researchers to perform advanced studies at a more granular level to deepen our understanding of different sports.
For complete surveys on how tracking data have transformed sports analytics, see @Macdonald2020Recreating, @Baumer2023Big, and @Kovalchik2023Player.

@@

In an attempt to foster analytics and innovate the game, the National Football League (NFL) introduced their player tracking system known as Next Gen Stats (NGS) in 2016 [@nfl2023ngs].
NGS uses radio frequency identification (RFID) chips placed in players' shoulder pads (and in the ball) to collect data at a rate of 10 frames per second.
The data captures real-time on-field information such as locations, speeds, and accelerations of all 22 players (and also the football).
While these data were initially only available for teams, media, and vendors, in December 2018 the NFL launched the inaugural edition of their annual Big Data Bowl (BDB) competition [@nfl2023big].

@@

```{r formation, fig.width=5, fig.height=4, fig.cap="Two common defensive alignments in football: 4-3 defense (top) and 3-4 defense (bottom). The dashed line represents the line of scrimmage separating the defense and offense."}
tibble(x = c(3:5, 3:6 - 0.5, c(2, 3.7, 4.3, 6)),
       y = c(1, 1, 1, 1.01, 1.01, 1.01, 1.01, 1.02, 1.02, 1.02, 1.02),
       pos = c("DE", "NT", "DE", "OLB", "ILB", "ILB", "OLB",
               "CB", "S", "S", "CB"),
       d = "3-4 Defense") |> 
  bind_rows(
    tibble(x = c(3:6, c(2.5, 4.5, 6.5), c(2, 4.1, 4.9, 7)),
           y = c(1, 1, 1, 1, 1.01, 1.01, 1.01, 1.02, 1.02, 1.02, 1.02),
           pos = c("DE", "DT", "DT", "DE", "OLB", "MLB", "OLB",
                   "CB", "S", "S", "CB"),
           d = "4-3 Defense") 
  ) |> 
  mutate(d = fct_relevel(d, "4-3 Defense", "3-4 Defense")) |> 
  ggplot(aes(x, y)) +
  geom_tile(fill = "white") +
  geom_label(aes(label = pos), size = rel(4)) +
  geom_hline(yintercept = 0.996, linetype = "dashed") +
  facet_wrap(~ d, scales = "free", ncol = 1) +
  coord_cartesian(ylim = c(0.99, 1.03)) +
  theme_light() +
  theme(strip.text = element_text(size = rel(1.2)),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank())
```

In this work, using data made available in the 2023 BDB, we present a novel approach to measure the performance of pass rushers. Relative to other aspects of American football, such as QB evaluation [@burke2019deepqb, @reyers2021quarterback], the literature on evaluating pass rushers is scarce. Below, we provide a brief overview of existing pass rush metrics.

@@

Perhaps the most commonly-known statistics for evaluating defensive linemen on pass rush plays are sacks, hits, and hurries, which are discretely observed at the play-level.
Officially tracked by the NFL since 1982, a sack is recorded when a defender tackles the QB behind the line of scrimmage before the QB releases a pass.
Other traditional box score statistics such as hits and hurries are collected by various outlets.
A hit is a collision between a defender and the opposing team's quarterback after the quarterback makes a throw.
A hurry represents an instance when a defender successfully disrupts without necessarily making direct contact with the QB and forces the QB to make a throw earlier than expected.
These are all simple binary measures of pass rush outcome for any given play.
However, for plays that do not result in the aforementioned outcomes (in particular, sack), there are still many intermediate defensive actions on the field within the play that are valuable and can be considered positive achievements.

In addition, the sum of sacks, hits, and hurries is often defined as pressures.
This is better than the individual counts to some extent, but suffers from problems of subjectivity (e.g., whether there is an actual hurry or not).
Pro football focus (PFF) defines a metric called pass-rush productivity (PRP), which is a minor modification from the aforementioned pressures metric (see Table \ref{tab:metrics}).
In particular, PRP gives twice as much weight to a sack relative to hurries and hits, which is a small upgrade to pressures.
However, the choice of weights is ad-hoc and still only considers binary outcomes, similar to the shortcomings of previous metrics.

@@

In this paper, we focus on the evaluation of defensive linemen in football.
We propose STRAIN, a metric for measuring pass rush effectiveness, inspired by the concept of strain rate in materials science.
Our statistic gives a continuous measure of pressure for every pass rusher on the football field over the course of an entire play.
This allows for the assessment of pass rush success even on plays that do not result in an observed outcome like a sack, hit, or hurry.
We view this as a major step forward for accurately evaluating defensive linemen performance.
We also demonstrate that STRAIN is a stable quantity over time and predictive of defensive pressure.
Additionally, we consider a multilevel model to estimate every pass rusher's contribution to the average STRAIN in a play while controlling for other positions like QB and pass blocker as well as various play-level information.
We note that although our focus in this paper is on pass rushers, our proposed approach can be extended to the evaluation of pass blockers in American football.

>>>>

In recent years, tracking data have replaced traditional box-score statistics and play-by-play data as the state of the art in sports analytics.
Numerous sports are collecting and releasing data on player and ball locations on the playing surface over the course of a game.
This multiresolution spatiotemporal source of data has provided exceptional opportunities for researchers to perform advanced studies at a more granular level to deepen our understanding of different sports.
For complete surveys on how tracking data have transformed sports analytics, see @Macdonald2020Recreating, @Baumer2023Big, and @Kovalchik2023Player.

@@

In an attempt to foster analytics and innovate the game, the National Football League (NFL) introduced their player tracking system known as Next Gen Stats (NGS) in 2016 [@nfl2023ngs].
NGS uses radio frequency identification (RFID) chips placed in players' shoulder pads (and in the ball) to collect data at a rate of 10 frames per second.
The data captures real-time on-field information such as locations, speeds, and accelerations of all 22 players (and the football).
While these data were initially only available for teams, media, and vendors, in December 2018 the NFL launched the inaugural edition of their annual Big Data Bowl (BDB) competition [@nfl2023big].

@@

```{r formation, fig.width=5, fig.height=4, fig.pos="t", fig.cap="Two common defensive alignments in football: 4-3 defense (top) and 3-4 defense (bottom). The dashed line represents the line of scrimmage separating the defense and offense."}
tibble(x = c(3:5, 3:6 - 0.5, c(2, 3.7, 4.3, 6)),
       y = c(1, 1, 1, 1.01, 1.01, 1.01, 1.01, 1.02, 1.02, 1.02, 1.02),
       pos = c("DE", "NT", "DE", "OLB", "ILB", "ILB", "OLB",
               "CB", "S", "S", "CB"),
       d = "3-4 Defense") |> 
  bind_rows(
    tibble(x = c(3:6, c(2.5, 4.5, 6.5), c(2, 4.1, 4.9, 7)),
           y = c(1, 1, 1, 1, 1.01, 1.01, 1.01, 1.02, 1.02, 1.02, 1.02),
           pos = c("DE", "DT", "DT", "DE", "OLB", "MLB", "OLB",
                   "CB", "S", "S", "CB"),
           d = "4-3 Defense") 
  ) |> 
  mutate(d = fct_relevel(d, "4-3 Defense", "3-4 Defense")) |> 
  ggplot(aes(x, y)) +
  geom_tile(fill = "white") +
  geom_label(aes(label = pos), size = rel(4)) +
  geom_hline(yintercept = 0.996, linetype = "dashed") +
  facet_wrap(~ d, scales = "free", ncol = 1) +
  coord_cartesian(ylim = c(0.99, 1.03)) +
  theme_light() +
  theme(strip.text = element_text(size = rel(1.2)),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank())
```

In this work, using data made available in the BDB 2023, we present a novel approach to measure the performance of pass rushers. Relative to other aspects of American football, such as QB evaluation [@burke2019deepqb, @reyers2021quarterback], the literature on evaluating pass rushers is scarce. Below, we provide a brief overview of existing pass rush metrics.

@@

Perhaps the most commonly-known statistics for evaluating defensive linemen on pass rush plays are sacks, hits, and hurries, which are discretely observed at the play-level.
Officially tracked by the NFL since 1982, a sack is recorded when a defender tackles the QB behind the line of scrimmage before the QB releases a pass.
Other traditional box score statistics such as hits and hurries are collected by various outlets.
A hit is a collision between a defender and the opposing team's quarterback after the quarterback makes a throw.
A hurry represents an instance when a defender successfully disrupts without necessarily making direct contact with the QB and forces the QB to throw the football earlier than expected.
These are all simple binary measures of pass rush outcome for any given play.
However, for plays that do not result in the aforementioned outcomes (in particular, sack), there are still many intermediate defensive actions on the field within the play that are valuable and can be considered positive achievements.

In addition, the sum of sacks, hits, and hurries is often defined as pressures.
This is better than the individual counts to some extent, but suffers from problems of subjectivity (e.g., whether there is an actual hurry or not).
Pro Football Focus (PFF) defines a metric called pass-rush productivity (PRP), which is a minor modification from the aforementioned pressures metric (see Table \ref{tab:metrics}).
In particular, PRP gives twice as much weight to a sack relative to hurries and hits, which is a small upgrade to pressures.
However, the choice of weights is ad-hoc and still only considers binary outcomes, similar to the shortcomings of previous metrics.

@@

In this paper, we focus on the evaluation of defensive linemen in football.
We propose STRAIN, a metric for measuring pass rush effectiveness, inspired by the concept of strain rate in materials science.
Our statistic gives a continuous measure of pressure for every pass rusher on the football field over the course of an entire play.
This allows for the assessment of pass rush success even on plays that do not result in an observed outcome like a sack, hit, or hurry.
We view this as a major step forward for accurately evaluating defensive linemen performance.
We also demonstrate that STRAIN is a stable quantity over time and predictive of defensive pressure.
Additionally, we consider a multilevel model to estimate every pass rusher's contribution to the average STRAIN in a play while controlling for other positions like QB and pass blocker as well as various play-level information.
We note that although our focus in this paper is on pass rushers, our approach can be extended to the evaluation of pass blockers in American football.

### 2023-05-17 paper/04-results.Rmd
arxiv submission

In contrast, Figure \ref{fig:fig_crosby_curves_unsucess} shows the feature curves for an unsuccessful pass rush attempt by the Raiders defense from the same game.
In this play, Broncos QB Teddy Bridgewater is well-protected by the offensive line and is able to release a long pass[^unsuccess] to a receiver.
We see that the STRAIN generated by Crosby is relatively small over the course of this play, compared to the previous play shown in Figure \ref{fig:fig_crosby_curves} which results in a sack.

@@

## Positional STRAIN curves {#sec:positional}

@@

Figure \ref{fig:fig_pos_curves} displays the average STRAIN by position for the first 40 frames (4 seconds) after the snap.
We observe a clear difference in STRAIN between edge rushers (OLB's and DE's) and interior linemen (DT's and NT's).
Specifically, edge rushers have higher STRAIN than interior linemen on average, as they are more easily able to approach the quarterback on the edge of the pocket versus, for instance, a nose tackle attacking the line head on.

@@

Since STRAIN is observed continuously for every play in our data, this allows us to aggregate across all frames played and compute the average STRAIN for NFL pass rushers over the course of the eight-week sample size, as discussed in Section \ref{sec:defn}.
Based on the clearly distinct patterns for different positions as previously observed, we evaluate interior pass rushers (NT's and DT's) separately from edge rushers (OLB's and DE's).
Tables \ref{tab:edge} and \ref{tab:interior} are leaderboards for the NFL's best edge and interior rushers (with at least 100 plays) rated by the average STRAIN across all frames for the first eight weeks of the 2021 regular season.
The tables also consist of the total number of hits, hurries, and sacks (determined from PFF scouting data) for each defender.

@@

Next, we examine different statistical properties of our proposed metric STRAIN.
Our focus here is to understand the stability and predictability of STRAIN, and we pose the following question:
How much does our metric vary from week to week?
In other words, is previous performance predictive of future performance based on our metric?
Below, we attempt the answer these questions, and the following results are for pass rushers with at least 100 snaps played during the first 8 weeks of the 2021 NFL regular season.

We first investigate the predictability of STRAIN as a measure of pressure.
In particular, we look at how well our metric correlates with a simple measure of pressure rate, defined as the total hits, sacks and hurries per snap.
Figure \ref{fig:fig_cor_pressure} is a scatterplot of average STRAIN and pressure rate over the course the provided 8-game sample, which reveals a fairly strong correlation ($r =0.625$) between the quantities.
Hence, defenders with high STRAIN values also tend to generate more pressure toward the quarterback.
Furthermore, the average STRAIN for the first 4 weeks of the 2021 season is more predictive of the last 4 weeks' pressure rate ($r=0.322$) than the first 4 weeks' pressure rate ($r=0.097$), as illustrated in Figure \ref{fig:fig_predictability}.

We also analyze the stability of STRAIN over time by comparing the average STRAIN across all frames played for the first and last four weeks of the 2021 NFL regular season.
It is apparent from Figure \ref{fig:fig_stability} that there is a strong positive correlation $(r = 0.854)$ for this relationship.
This means that STRAIN is a highly stable football metric over the provided 8-week time window, and pass rushers appear to carry their STRAIN values with them from week to week.
Overall, STRAIN performs well in both explaining defensive pressure on the field and predicting future performance of pass rushers.

```{r}
#| label: fig_cor_pressure
#| fig.cap: "Relationship between average STRAIN and pressure rate (total hits, sacks, and hurries per snap) over the first 8 weeks of the 2021 NFL season. There is a moderately strong association between average STRAIN and pressure rate ($r =0.625$). Results shown here are for pass rushers with at least 100 snaps play over the 8-week data."
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "04_fig_cor_pressure.R"))
fig_cor_pressure
```

```{r}
#| label: fig_predictability
#| fig.cap: "Relationships between pressure rate for the last 4 weeks of the 2021 NFL season and first 4 weeks' pressure rate (left) and average STRAIN (right). STRAIN is more predictive ($r=0.322$) of future pressure rate than previous pressure rate itself ($r=0.097$). Results shown here are for pass rushers with at least 100 snaps play over the 8-week data."
#| fig.width: 6.5
#| fig.height: 3
#| fig.show: "hold"
source(here("scripts", "07_fig_predictability.R"))
fig_predictability
```

```{r}
#| label: fig_stability
#| fig.cap: "Relationship between average STRAIN for the last and first 4 weeks of the 2021 NFL season. A strong linear correlation ($r = 0.854$) demonstrates that STRAIN is a highly stable metric over time. Results shown here are for pass rushers with at least 100 snaps play over the 8-week data."
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "05_fig_stability.R"))
fig_stability
```

@@

Moreover, we observe statistically significant differences among the pass rush and pass block positions in most cases, while controlling for other variables.
The coefficient estimates for the pass rush position terms reveal that players with positions closer to the line of scrimmage (DT and NT) appear to generate less STRAIN (relative to DE) than those lining up further back, which is consistent with our results in Section \ref{sec:positional}.
For blockers, centers are those that absorb the most pressure on average, more than guards and other offensive positions (compared to the baseline level, tackles).

>>>>

In contrast, Figure \ref{fig:fig_crosby_curves_unsucess} shows the feature curves for an unsuccessful pass rush attempt by the Raiders defense from the same game.
In this play, Broncos QB Teddy Bridgewater is well-protected by the offensive line and is able to release a long pass[^unsuccess] to a receiver.
We see that the STRAIN generated by Crosby is relatively small over the course of this play, compared to the previous play (as shown in Figure \ref{fig:fig_crosby_curves}) which results in a sack.

@@

## Positional STRAIN Curves {#sec:positional}

@@

Figure \ref{fig:fig_pos_curves} displays the average STRAIN by position for the first 40 frames (4 seconds) after the snap.
We observe a clear difference in STRAIN between edge rushers (OLBs and DEs) and interior linemen (DTs and NTs).
Specifically, edge rushers have higher STRAIN than interior linemen on average, as they are more easily able to approach the quarterback on the edge of the pocket versus, for instance, a nose tackle attacking the line head on.

@@

Since STRAIN is observed continuously for every play in our data, this allows us to aggregate across all frames played and compute the average STRAIN for NFL pass rushers over the course of the eight-week sample size, as discussed in Section \ref{sec:defn}.
Based on the clearly distinct patterns for different positions as previously observed, we evaluate interior pass rushers (NTs and DTs) separately from edge rushers (OLBs and DEs).
Tables \ref{tab:edge} and \ref{tab:interior} are leaderboards for the NFL's best edge and interior rushers (with at least 100 plays) rated by the average STRAIN across all frames for the first eight weeks of the 2021 regular season.
The tables also consist of the total number of hits, hurries, and sacks (determined from PFF scouting data) for each defender.

@@

Next, we examine different statistical properties of our proposed metric STRAIN.
Our focus here is to understand the stability and predictability of STRAIN, and we pose the following question:
How much does our metric vary from week to week?
In other words, is previous performance predictive of future performance based on our metric?
Below, we attempt the answer these questions, and the following results are for pass rushers with at least 100 snaps played during the first eight weeks of the 2021 NFL regular season.

We first investigate the predictability of STRAIN as a measure of pressure.
In particular, we look at how well our metric correlates with a simple measure of pressure rate, defined as the total hits, sacks and hurries per snap.
Figure \ref{fig:fig_cor_pressure} is a scatterplot of average STRAIN and pressure rate over the course the provided eight-game sample, which reveals a fairly strong correlation ($r =0.625$) between the quantities.
Hence, defenders with high STRAIN values also tend to generate more pressure toward the quarterback.
Furthermore, the average STRAIN for the first four weeks of the 2021 season is more predictive of the last four weeks' pressure rate ($r=0.322$) than the first four weeks' pressure rate ($r=0.097$), as illustrated in Figure \ref{fig:fig_predictability}.

We also analyze the stability of STRAIN over time by comparing the average STRAIN across all frames played for the first and last four weeks of the 2021 NFL regular season.
It is apparent from Figure \ref{fig:fig_stability} that there is a strong positive correlation $(r = 0.854)$ for this relationship.
This means that STRAIN is a highly stable football metric over the provided eight-week time window, and pass rushers appear to carry their STRAIN values with them from week to week.
Overall, STRAIN performs well in both explaining defensive pressure on the field and predicting future performance of pass rushers.

```{r}
#| label: fig_cor_pressure
#| fig.cap: "Relationship between average STRAIN and pressure rate (total hits, sacks, and hurries per snap) over the first eight weeks of the 2021 NFL season. There is a moderately strong association between average STRAIN and pressure rate ($r =0.625$). Results shown here are for pass rushers with at least 100 snaps played over the eight-week data."
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "04_fig_cor_pressure.R"))
fig_cor_pressure
```

```{r}
#| label: fig_predictability
#| fig.cap: "Relationships between pressure rate for the last 4 weeks of the 2021 NFL season and first four weeks' pressure rate (left) and average STRAIN (right). STRAIN is more predictive ($r=0.322$) of future pressure rate than previous pressure rate itself ($r=0.097$). Results shown here are for pass rushers with at least 100 snaps played over the eight-week data."
#| fig.width: 6.5
#| fig.height: 3
#| fig.show: "hold"
source(here("scripts", "07_fig_predictability.R"))
fig_predictability
```

```{r}
#| label: fig_stability
#| fig.cap: "Relationship between average STRAIN for the last and first four weeks of the 2021 NFL season. A strong linear correlation ($r = 0.854$) demonstrates that STRAIN is a highly stable metric over time. Results shown here are for pass rushers with at least 100 snaps played over the eight-week data."
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "05_fig_stability.R"))
fig_stability
```

@@

Moreover, we observe statistically significant differences among the pass rush and pass block positions in most cases, while controlling for other variables.
The coefficient estimates for the pass rush position terms reveal that players with positions closer to the line of scrimmage (DTs and NTs) appear to generate less STRAIN (relative to DEs) than those lining up further back, which is consistent with our results in Section \ref{sec:positional}.
For blockers, centers are those that absorb the most pressure on average, more than guards and other offensive positions (compared to the baseline level, tackles).

### 2023-05-17 paper/05-discussion.Rmd
arxiv submission

# Discussion {#sec:discussion}
In this work, we have proposed STRAIN - a simple and interpretable statistic for evaluating pass rushers - with higher values corresponding to greater pass rushing ability. We demonstrated that a pass rusher's average STRAIN is both stable and more predictive of future pressure events than using the player's previously observed pressure events. This is analogous to the use of exit velocity in baseball, a predictive measurement that avoids the noisy nature of observed outcomes, emphasizing how the opportunity of working with player-tracking data can lead to the development of insightful metrics in American football.

@@

Moreover, although we focus solely on pass rushers in this paper, STRAIN can be easily extended to the assessment of pass blockers as a unit.
This can be accomplished through the aforementioned APM regression or by simply looking at quantities such as the total STRAIN or the maximum STRAIN per frame aggregated across the entire play.
It is also possible to apply STRAIN to assess individual offensive pass blockers, provided that a method of matching blockers to rushers was developed.
Furthermore, compared to existing metrics, STRAIN measures pass rush effectiveness for every play continuously over time, which is at a much more granular level than considering whether the play resulted in a binary outcome such as a sack.
There is ample opportunity for working with the complete STRAIN trajectories via functional data analysis to help understand how STRAIN affects offensive production.

>>>>

# Discussion {#sec:discussion}
In this work, we have proposed STRAIN---a simple and interpretable statistic for evaluating pass rushers---with higher values corresponding to greater pass rushing ability.
We demonstrated that a pass rusher's average STRAIN is both stable and more predictive of future pressure events than using the player's previously observed pressure events.
This is analogous to the use of exit velocity in baseball, a predictive measurement that avoids the noisy nature of observed outcomes, emphasizing how the opportunity of working with player tracking data can lead to the development of insightful metrics in American football.

@@

Moreover, although we focus solely on pass rushers in this paper, STRAIN can also be applied to the assessment of pass blockers as a unit.
This can be accomplished through the aforementioned APM regression or by simply looking at quantities such as the total STRAIN or the maximum STRAIN per frame aggregated across the entire play.
It is also possible to apply STRAIN to assess individual offensive pass blockers, provided that a method of matching blockers to rushers was developed.
Furthermore, compared to existing metrics, STRAIN measures pass rush effectiveness for every play continuously over time, which is at a much more granular level than considering whether the play resulted in a binary outcome such as a sack.
There is ample opportunity for working with the complete STRAIN trajectories via functional data analysis to better understand the impact of STRAIN on offensive production in American football.
